An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-01 tex/paper.tex
Putting myself first in the list (as corresponding)
Remove back refs in bibliography.
Final checks and adding acknowledgements etc.

% Nicer bibliography management
\usepackage[backend=biber, backref=true, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
        % Core devs (alphabetic order of last name)
        \item Campbell, Owen
        \item Harper, Marc
        \item Knight, Vincent
        \item Langner, Karol
        % All devs (alphabetic order of last name)
        \item Campbell, James
        \item Campbell, Thomas
        \item Carney, Alex
        \item Chorley, Martin
        \item Davidson-Pilon, Cameron
        \item Glass, Kristian
        \item Ehrlich Tom{\'a}{\v s}
        \item Jones, Martin
        \item Koutsovoulos, Georgios
        \item Marissa, Holly
        \item M{\"u}ller, Jochen
        \item Palmer, Geraint
        \item Slavin, Paul
        \item Standen, Timothy
        \item Visintini, Luis
        \item Molden, Karl
    \end{enumerate}
\end{multicols}

@@

With a growing collection of 120 strategies, the library is a also a
platform for an original tournament that, in itself, is of interest to the
game theoretic community.

@@

As stated in the Overview, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

To date the library has had contributions from 24 contributors from a variety of
backgrounds. These contributions have been in terms of strategies. One strategy
is the creation of an undergraduate mathematics student with little prior
knowledge of programming. Multiple other strategies were written by a 15 year old
secondary school student. As well as these strategy contributions, vital
architectural improvements to the library itself have also been received. You
can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.

@@

This library has the potential to be a common standard for research in to the
iterated Prisoner's dilemma. In particular, having a large library of
tested strategies readily available for experimentation is of high value to the
research community.

This has been evidenced by the work described: the library has already shown
it's potential for reuse.

\section*{Conclusion}\label{sec:conclusion}

@@

The ability to have readily available a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theoretic community.

>>>>

% Nicer bibliography management
\usepackage[backend=biber, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
        % Core devs (alphabetic order of last name after Vince as corresponding
        % goes first).
        \item Knight, Vincent
        \item Campbell, Owen
        \item Harper, Marc
        \item Langner, Karol
        % All devs (alphabetic order of last name)
        \item Campbell, James
        \item Campbell, Thomas
        \item Carney, Alex
        \item Chorley, Martin
        \item Davidson-Pilon, Cameron
        \item Glass, Kristian
        \item Ehrlich Tom{\'a}{\v s}
        \item Jones, Martin
        \item Koutsovoulos, Georgios
        \item Marissa, Holly
        \item M{\"u}ller, Jochen
        \item Palmer, Geraint
        \item Slavin, Paul
        \item Standen, Timothy
        \item Visintini, Luis
        \item Molden, Karl
    \end{enumerate}
\end{multicols}

@@

With a growing collection of 122 strategies, the library is a also a
platform for an original tournament that, in itself, is of interest to the
game theoretic community.

@@

As stated in the \textbf{Introduction}, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

To date the library has had contributions from 24 contributors from a variety
of backgrounds. These contributions have been in terms of strategies. One
strategy is the creation of an undergraduate mathematics student with little
prior knowledge of programming. Multiple other strategies were written by a 15
year old secondary school student. Both of these students are authors of this
paper. As well as these strategy contributions, vital architectural
improvements to the library itself have also been received. You can see an
overview of the structure of the source code in Figure~\ref{fig:overview}.

@@

The ability to have readily available a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theoretic community.
This has been evidenced by the work described: the library has already shown
it's potential for reuse.

\section*{Conclusion}

@@

\section*{Acknowledgements}

The authors would like to thank all contributors. Also, they thank
Robert Axelrod himself for his well wishes with the library.

\section*{Competing interests}

The authors declare that they have no competing interests.
